\documentclass[helvetica,english,nologo,notitle,totpages,utf8]{europecv2013}
\usepackage{graphicx}
\usepackage[a4paper,top=1.2cm,left=1.2cm,right=1.2cm,bottom=2.5cm]{geometry}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{bibentry}

\graphicspath{ {images/}} %upload your signature to this file


\ecvname{Richard Gunning}
%\ecvaddress{16 Sladwell Close, Grantchester, Cambridgeshire, CB2 9NP United Kingdom}
\ecvaddress{The Forbes Building, 19 Austin Drive, Trumpington, Cambridgeshire, UK, CB2 9BB}

%\ecvtelephone{+44 7557090952}
\ecvemail{rjgunning@gmail.com}
%\ecvlinkedin{\href{http://it.linkedin.com/in/rjgunning}{linkedin.com/in/rjgunning}}
\ecvhomepage{\href{http://rjgunning.com}{rjgunning.com}}
\ecvskype{r.gunning}
%\ecvgender{Male}
%\ecvdateofbirth{22 December 1989}

%\ecvfootnote{© European Union, 2002-2013 | http://europass.cedefop.europa.eu}
%\ecvbeforepicture{\raggedleft}
%\ecvpicture[width=2.5cm]{fototessera}
%\ecvafterpicture{\ecvspace{-37mm}}

\begin{document}
\selectlanguage{english}

\begin{europecv}
\ecvpersonalinfo[10pt]

\ecvposition{Job applied for}{Front-End Web Developer}
%\ecvitem[10pt]{Summary}{I am currently investigating the relationship between epigenetic factors and genetic splicing as part of a  BBSRC Doctoral Training Programme PhD project at the University of Cambridge. As part of my PhD programme, the BBSRC will fully fund a 3 month internship which I would like to undertake at Oxford Nanopore. I am interested in the technology being developed at Oxford Nanopore and would like to learn how to work with the data produced by MinION. I am keen to apply the skills I have developed academically in an industrial setting. }

\ecvitem[10pt]{Summary}{I am completing a PhD in Bioinformatics and moving into web development. I have experience as a full-stack developer, building cross-platform, responsive websites, from working as MCR computing officer on the Clare College MCR committee and as creative director for History to the Public.}
%Currently completing a Bioinformatics PhD at the Wellcome Trust Sanger Institute on the relationship between epigenetic factors and genetic splicing. I developed an interest in web design during the course of my PhD from acting as MCR Computing Officer for Clare College. I am responsible for the redesign of the Clare College MCR website in 2014 and built an AngularJS punts booking website for them in June 2016. I am currently working on a new formal hall booking website. Along with other Graduates, we launched History To The Public in 2014 for which I was responsible for the web design and upkeep. I am now looking at moving fully into web design.}

\ecvitem[10pt]{Computer skills}{
\textbf{Languages}: HTML5, CSS3, PhP, Javascript, AngularJS, JQuery, MySQl , MQL4, MQL5, R, Bash, Python, Perl.\par
\textbf{Version Control}: Git
%\textbf{Group Communication}: Trello, Slack
}

\ecvsection{Work experience}

\ecvworkexperience{May 2014 -- Present}{MCR Computing Officer}{Clare College Cambridge}{Member of The Clare College Graduate Society Committee (MCR)\par
- Full-stack web development for Clare College Punts booking website. Created an AngularJS front-end wi PhP REST back-end. (screenshots and design notes can be seen here: \href{http://rjgunning.com/clarepunts.html}{http://rjgunning.com/clarepunts.html})\par
- Front-end redseign of Clare MCR website (\href{http://mcr.clare.cam.ac.uk}{http://mcr.clare.cam.ac.uk})
}

\ecvworkexperience{December 2014 -- Present}{Creative Director}{History To The Public}{As creative director, I am responsible for the design, layout and upkeep of the \href{http://historytothepublic.org}{historytothepublic.org} website as well as producing content.}

\ecvworkexperience{June 2015 -- June 2017}{Clare College Boat Club Webmaster}{Clare College Cambridge}{
Maintenance of Clare College Boat Club website (\href{http://www.clareboatclub.org.uk/}{http://www.clareboatclub.org.uk/})}

\ecvworkexperience{November 2016 -- January 2017}{Intern}{Netcom Consulting, Inc.}{3 Month Internship as part of BBSRC DTP Professional Internship for PhD Students (PIPS). The main objectives of the project was to develop a FOREX automated trading system for trading multiple currency pairs on MetaTrader 4 and MetaTrader 5 platforms. Programming in MQL4 and MQL5 languages.} 

\ecvworkexperience{May 2015 -- May 2017}{MCR Secretary}{Clare College Cambridge}{Member of The Clare College Graduate Society Committee (MCR)\par
- Managerial role with organisation of regular committee and graduate body meetings.\par
- Rewrote the MCR Constitution\par
- Established and maintained Social media accounts on various platforms including Twitter and Facebook and Managed a weekly newsletter }

%\ecvworkexperience{June 2014 -- June 2015}{Clare College Boat Club Men's Captain}{Clare College Cambridge}{Leading the Men's squad which included organising: Training schedules, Coaches, Race entries, Training camps}

\ecvworkexperience{July 2012 -- September 2012}{Internship in Ewan Birney's group}{European Bioinformatics Institute}{
Topic: `Automated Phenotypic measurements of Spines in Healthy Human individuals From MRI scans'}

%\ecvworkexperience{June 2011 -- September 2011\\ June 2010 -- September 2010}{Student Laboratory Assistant}{BlueGnome, Cambridge}{}{- Performed Degenerate oligonucleotide primed PCR to separate human DNA from bacterial plasmid as part of a project to regenerate the DOP library.\par- Microarray printing.}




\ecvsection{Education and training}

\ecveducation{2014 -- Present}{Doctor of Philosophy}{University of Cambridge, United Kingdom}{BBSRC Doctoral Training Programmme\par PhD Thesis Title: `Examining the impact of the epigenetic landscape on splicing events'\par Working on Unix systems in multiple languages including BASH, Python, R and developing shiny webapps}{}

\ecveducation{2013 -- 2014}{Master of Research}{University of Cambridge, United Kingdom}{BBSRC Doctoral Training Programmme\par Rotation projects in the labs of Dr Karen Lipkow (Babraham Institute) and Dr Anne Ferguson-Smith (Department of Genetics)}{}

\ecveducation{2012 -- 2013}{Master of Science in Bioinformatics}{King's College London, London United Kingdom}{MSC Individual project - `Effect of genetic factors on a mitochondrial metabolic network model'}{}

\ecveducation{2009 -- 2012}{Bachelor of Science in Biochemistry}{King's College London, London United Kingdom}{}{}

\ecvsection{Personal skills}

\ecvmothertongue[20pt]{English}
%\ecvlanguageheader
%\ecvlanguage{French}{C1}{C2}{B2}{C1}{C2}
%\ecvlastlanguage{German}{A2}{A2}{A2}{A2}{A2}
%\ecvlanguagefooter[10pt]

\ecvitem[10pt]{Communication skills}{
\textbf{Teamwork}: I work in various types of teams from research teams to committees to rowing teams. Good teamwork skills were an important part of the Netcom Consulting, Inc internship, where I worked as part of a small team on the development of software. Good teamwork skills allowed us to bounce ideas off each other and effectively split the project into manageable pieces. As part of HTTP, I manage and maintain online communication channels for a team of 10 writers. I coached my university rowing team at King's College London and was men's captain of the Clare College rowing team at Cambridge\par
\textbf{Public Communication}: I am an organising member of the \href{http://historytothepublic.org}{History To The Public} and often write and edit articles designed to bridge the gap between academics and the public.
}

\ecvitem[10pt]{Organisational / managerial skills}{
\textbf{Conference Organiser}: Annual EBI-Sanger-Cambridge PhD Symposium (eSCAMPS) on 18th February 2015\par
\textbf{Committee Secretary}: Clare College MCR Secretary involves the regular organisation of meetings as well as the managment and file organisation of the committee documents.}

%\ecvitem[10pt]{Computer skills}{
%\textbf{Languages}: HTML5, CSS3, PhP, Javascript, AngularJS, JQuery, MySQl , MQL4, MQL5, R, Bash, Python, Perl.\par
%\textbf{Version Control}: Git\par
%\textbf{day-to-day}: My PhD makes extensive use of Bash, Python, R and Perl\par
%\textbf{Webmaster}: \href{http://mcr.clare.cam.ac.uk}{Clare College MCR}, \href{http://historytothepublic.org}{History To The Public}, \href{http://www.clareboatclub.org.uk}{Clare College Boat Club}, \href{http://www.clareity.co.uk}{Clareity}\par
%}

%\ecvitem[10pt]{Other skills}{Enjoy all sports particularly rowing and running.}

%\ecvitem[10pt]{Driving licence}{A, B}


%\bibliographystyle{plain}
%\nobibliography{publications-en}

%\ecvsection{ADDITIONAL INFORMATION}

%\ecvitem{Publications}{\bibentry{pub1}}

%\ecvitem{References}{References available on request}


\ecvsection{Websites}
 \ecvitem{\href{https://github.com/Clare-MCR/ClarePunts}{github.com/Clare-MCR/ClarePunts}}{In 2016, Clare College combined their punt committees and tasked me with creating them a new responsive website with an emphasis on being mobile friendly. For this I developed a PhP REST server back-end with an Angular JS front-end. Screenshots of the website can be seen here (\href{http://rjgunning.com/clarepunts.html}{rjgunning.com/clarepunts.html}) as the main site is behind a College login.}
    
\ecvitem{\href{http://mcr.clare.cam.ac.uk}{mcr.clare.cam.ac.uk}}{I redesigned the Clare College MCR website in 2014. The Clare College MCR website is a Wordpress website. For this site, I wrote a custom child-theme for the site. I also created a Wordpress PhP plugin for streamlining the creation of the weekly MCR newsletter, which collates a series of posts and sends them out as a mass email to the graduate community.}
    
\ecvitem{\href{http://historytothepublic.org}{historytothepublic.org}}{The final project I am proud to have worked on is History to the Public. Along with other Graduates from several Universities, we launched History To The Public in 2014, a public outreach history blog project. I setup this website with a Wordpress back-end then developed a custom child-theme for the website. For this project I also created an automated Twitter bot which periodically tweets one of the past articles from the blog.}


\ecvitem{References}{
%\parbox[t]{0.33\textwidth}{Dr. David Adams \\ \href{mailto:david.adams@sanger.ac.uk}{david.adams@sanger.ac.uk} \\Wellcome Trust Sanger Institute,\\ Hinxton,\\ Saffron Walden\\ CB10 1SA} 
\parbox[t]{0.33\textwidth}{Jason Randall\\ \href{mailto:jjr37@cam.ac.uk}{jjr37@cam.ac.uk} \\Clare College,\\ Cambridge,\\ CB2 1TL} 
\parbox[t]{0.33\textwidth}{Tero Sahrakorpi \\ \href{mailto:tero@promo2cell.com}{tero@promo2cell.com}\\ Netcom Consulting, Inc.,\\ 1500 N University Dr, \\\#115,
\\Coral Springs,\\
FL 33071, USA}
}
\end{europecv}
\end{document} 
