\documentclass[helvetica,english,utf8]{coverletter2013}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[a4paper,top=1.7cm,left=1.5cm,right=1.2cm,bottom=1.5cm]{geometry}
\usepackage[english]{babel}

\usepackage{wrapfig}

\graphicspath{ {images/}} %upload your signature to this file


\eclname{Richard Gunning}
\ecladdress{16 Sladwell Close, Grantchester, Cambridgeshire, CB2 9BB United Kingdom}
\ecltelephone{+44 7557090952}
\eclemail{rjgunning@gmail.com}
%\ecllinkedin{\href{http://it.linkedin.com/in/rjgunning}{linkedin.com/in/rjgunning}}
%\eclhomepage{\href{http://rjgunning.com}{rjgunning.com}}
%\eclskype{r.gunning}

\begin{document}
\selectlanguage{english}

\eclpersonalinfo

\ecladdressee{ Johanna McEntyre, EMBL-EBI}{Wellcome Trust Genome Campus}{Hinxton, Cambridge}{}

\eclcitydatesubject{Cambridge}{\today}{Front-End Web Developer}

\eclopeningsalutation{Dear Johanna McEntyre}

\eclmaincontent
{I am applying for the position of Front-End Web Developer at EMBL-EBI, which I saw advertised on LinkedIn. 
I am currently completing a Bioinformatics PhD at the Wellcome Trust Sanger Institute on the relationship between epigenetic factors and genetic splicing, due to submit by September. I developed an interest in web design during the course of my PhD from acting as MCR Computing Officer for Clare College Cambridge to becoming a self-taught full-stack web developer. 
\bigskip}
% You need to tell them why they want to want you. What are you offering them? Why do you think you'd be a great fit for this EBI team? (Why you are interested in this role and this particular company. If you are currently a postdoc, you might also use this space to explain why you are making a career change from academia.)

{I have several years of front-end and back-end web development experience and enjoy learning new frameworks and better practices. Throughout my PhD, I have been doing an increasing amount of web development through my roles of MCR (Middle Combination Room) Computing Officer and Creative Director for History to the Public. As I finish my PhD, I wish moving into web development and take up the role as front-end web developer. From my time as an intern in Ewan Birney's group, I have experience of the friendly and inclusive atmosphere at EMBL-EBI. My experience from studying a PhD in Bioinformatics should also be a bonus in letting me understand the work being done by the team and letting me integrate into the team quickly.}

% Why the employer should be interested in you. Pick some highlights from your experience which are most relevant to the role’s requirements. (The letter does not need to cover everything in your CV.) 

{I would be an excellent for for the Literature Services Team because of my dedication and passion of creating web-based interfaces and being a team player. From my time as the Computing Officer at Clare College, webmaster at Clare College Boat Club and Creative Director at History to the Public, I have had the opportunities to work on a variety of web projects built with a range of frameworks. These have included python Flask websites, Wordpress websites, PhP5 websites and simple HTML5 static websites. In the process of maintaining these sites I have learnt both the platforms, frameworks and the different coding styles to both maintain them and update the legacy code in them. I am currently working on the development of a new Formal Hall booker for the Clare College MCR. This website will have an AngularJS front-end and a PhP REST server back-end which I hope to complete over summer. Collaboration has always been an important part of my work flow, and working with others has been a vital part of my experience as a rowing captain and being a a part of Clare MCR Executive Committee. I always enjoy learning new things and would enjoy the chance to improve my front-end web development among a team of professionals at EMBL-EBI.}


\eclclosingsalutation{Please do not hesitate to be in contact if you have any questions.\par Yours sincerely}

\eclsignature{signature} % signature image file

\end{document} 